### 2020-03-12 Article.tex
Coronavirus

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}

@@

\subsection{General notation}

Given a positive natural number $n$, we will write
$[n]$ to denote the set ${1,2,\dots,n}$.\par
Given a set $S$ and a natural number $k\in \N$
we will use $\binom{S}{k}$ to denote the set of 
subsets of $S$ whose size is $k$. \par
Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$(x_1,\dots,x_a)$ we define $g(x_1,\dots,x_a)=
(x_{g(1)},\dots,x_{g(a)})$.
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$. Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. The notation $(x_1,\dots, x_a)$ 
will be reserved 
to ordered tuples while 
$[x_1,\dots,x_a]$ will denote an ordered tuple modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par
We will denote ordered lists of elements by $\overbar{x}:=x_1,\dots,x_a$. 
This way, expressions like $(\overbar{x})$ or $[\overbar{x}]$ would mean 
$(x_1,\dots,x_a)$ and $[x_1,\dots,x_a]$ respectively.
Sometimes we will directly write $\overbar{x}$ without specifying the list
it names nor its length when it is understood or not relevant.
\par
Given two real functions over the natural numbers 
$f,g:\N \rightarrow \R$ we will write $f=O(g)$ to 
mean that there exists some constant $C\in \R$
such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
as usual.
If $g(n)\neq 0$ for sufficiently large values of $n$ then
we will write $f\simeq g$ if $\Ln \frac{f(n)}{g(n)}=1$.\par

@@

A relational vocabulary $\sigma$ is a collection of
relation symbols $(R_1,\dots, R_m,\dots)$
where each relation symbol $R_i$ has associated a natural $a_i$
number called its arity.
A $\sigma$-structure $\mathfrak{A}$ is composed of
a set $A$, called the universe of $\mathfrak{A}$, equipped with
relations $R_1^{\mathfrak{A}}\subseteq A^{a_1},
\dots, R_m^{\mathfrak{A}}\subseteq A^{a_m}$. When $\sigma$
is understood we may refer to $\sigma$-structures as relational
structures or simply as structures.
A structure is called finite if its universe is a finite set. \par

In the first order language $FO[\sigma]$ with signature $\sigma$ 
formulas are formed by variables $x_1,\dots, x_i,\dots$,
the relation symbols in $\sigma$, the equal symbol $=$,
the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
the existential and universal quantifiers $\exists, \forall$, and
the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
follows.
\vspace*{-0.2em}
\begin{itemize}[topsep=1pt, itemsep=1pt]
	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
	is a relation symbol in $\sigma$ with arity $a$, belongs to $FO[\sigma]$.
	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
	belongs to $FO[\sigma]$.
	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
	does not appear bounded
	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
\end{itemize}  
We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overbar{y}$
instead of  
$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
the quantifier $\exists$.

We define the set of free variables of a formula as usual. 
We will use the notation $\phi(\overbar{y})$ to refer to a 
formula $\phi\in FO[\sigma]$
to denote that its free variables are the ones in $\overbar{y}$.
Formulas with no free variables are called sentences and 
formulas with no quantifiers are called open formulas. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
formula, $\overbar{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overbar{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item Positive natural numbers $t$, $\overbar{a}=a_1,\dots, a_t$, with 
	all the $a_i$'s greater than $1$.\

	\item A relational vocabulary $\sigma=\{\overbar{R}\}$, with
	$\overbar{R}=R_1,\dots, R_t$ such that $a_i$ is the arity of
	$R_i$.

	\item 
	Groups $\overbar{\Phi}=\Phi_1,\dots,\Phi_t$
	such that each $\Phi_i$ is consists of 
	permutations on $[a_i]$ with the usual 
	composition as its operation.

	\item 
	Sets $\overbar{P}=P_1, \dots, P_t$ satisfying 
	$P_i\subseteq \binom{[a_i]}{2}$

@@

We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
as "multi-hypergraphs" with
$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
, are invariant under permutations in $\overbar{\Phi}$ resp., 
and do 
not contain repetitions of vertices in the positions given by
$\overbar{P}$ resp. We make this observation formal in the 
following definitions:

@@

We define the class $\mathcal{C}$ as the 
class of $\sigma$-structures that
satisfy the 
following axioms: 
\begin{itemize}
	\item \textit{Symmetry axioms}: For each $1\leq s \leq t$ and
	each $g\in \Phi_s$:
	\[ \forall x_1,\dots, x_{a_s} \big(  R_s(x_1,\dots, x_{a_s})
	\iff R_s(x_{g(1)},\dots,x_{g(a_s)}) \big)    \]
	\item \textit{Anti-reflexivity axioms}: For each 
	$1\leq s \leq t$ and $\{i,j\}\in P_s$
	\[ \forall x_1,\dots, x_{a_s} 
	\big( (x_i=x_j) \implies \neg R_s(x_1,\dots, x_{a_s})
	\big)\]
	\end{itemize}

We can think of structures in  $\mathcal{C}^{\sigma}_{\overbar{\Phi},\overbar{P}}$
as "multi-hypergraphs" with
$t$ edge sets whose edges are of sizes $\overbar{a}$ respectively
, are invariant under permutations in $\overbar{\Phi}$ resp., 
and do 
not contain repetitions of vertices in the positions given by
$\overbar{P}$ resp. We make this observation formal in the 
following definitions:

\begin{definition} 
	Let $V$ be a set, $a$ be a positive natural number,
	$\Phi$ be a group of permutations over $[a]$ and
	$P\subseteq \binom{[a]}{2}$. 
	We define the \textbf{total
	edge set over $V$ with edge size $a$, symmetry group $\Phi$ and 
	anti-reflexivity restrictions $P$} as the set
	\[ E^{V}_{a,\Phi,P}= (V^a/\Phi) \setminus \{ [x_1,\dots,x_a]  
	\,| \,
	x_1,\dots,x_a\in V \, \wedge \, x_i=x_j \text{ for some } \{i,j\}\in P \}. \]
\end{definition}

That is, $E^{V}_{a,\Phi,P}$ contains all the ``tuples modulo the permutations
in $\phi$" excluding those that contain some repetition of vertices in
the positions given by $P$.

\begin{definition} 
A \textbf{ multi-hypergraph with
with $t$ edge sets, edge sizes given by
$\overbar{a}$,
symmetry groups $\overbar{\Phi}$, 
and anti-reflexivity restrictions $\overbar{P}$}
is a pair $G=(V(G),\overbar{E(G)})$,
where $\overbar{E(G)}=E_1(G),\dots, E_t(G)$ and
for each $i$, $E_i(G) \subseteq E^{V}_{a_i,\Phi_i,P_i}$.
\end{definition}

For the sake of word economy the expression 
``multi-hypergraph with
$t$ edge sets, with edge sizes given by $\overbar{a}$,
symmetry groups $\overbar{\Phi}$, and anti-reflexivity 
restrictions $\overbar{P}$" 
will be replaced simply by ``hypergraph ". The word 
``hypergraph" will not hold
any other meaning than this for the rest 
of this writing except for the places
where it is explicitly stated.  \par

Hypergraphs, as we have defined them, 
can be naturally interpreted as
structures from $\mathcal{C}^
{\sigma}_{\overbar{\Phi},\overbar{P}}$ 
in the following way: 
given $G=(V,\overbar{E})$,
we consider $V$ to be the universe of
 $G$, and for any $i$ we define
$R_i^G\subseteq V^{a_i}$ as the set such that
$(\overbar{x})\in V^{a_i}$, 
$(\overbar{x})\in R_i^G$ if and only if 
$[\overbar{x}]\in E_i$. Under 
this interpretation hypergraphs, by definition,
satisfy the symmetry and anti-reflexivity
axioms given above. It is also easy to
see that this interpretation induces
a one-to-one identification between 
structures in $\mathcal{C}^{\sigma}_{\overbar{\Phi}
,\overbar{P}}$ and hypergraphs. \par

We will use standard nomenclature and notation
from graph theory. This way, we will call vertex set
to $V(G)$ and vertices to its elements. Likewise, each of 
the $E_i(G)$'s will be called an edge set and its elements, 
edges. Given an edge set $E_i(G)$, the index $i$ will
be called its color, and the number
$a_i$ its size. Thus, we will say that
an edge $e\in E_i(G)$ has color $i$ and size
$a_i$.

Given a set of vertices $U\subseteq V(G)$, 
we will denote by $G[U]$ the hypergraph induced
by $G$ on $U$. That is, $G[U]$ is an hypergraph
$H=(V(H),\overbar{E(H)})$ such that $V(H)=U$ and
for any list $\overbar{v}$ of vertices in $U$,
$[\overbar{v}]\in E_i(H)$ if and only if 
$[\overbar{v}]\in E_i(G)$.
\par

An homomorphism between two hypergraphs $G$ and $H$ 
a map $f:V(G)\rightarrow V(H)$ that sends edges 
from $G$ to edges in $H$ of the same color. That is,
if vertices $v_1,\dots, v_{a_i}$ form an edge 
$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
If $f$ is injective then it is called a monomorphism. 
If $f$ is bijective and its inverse is also an homomorphism 
between $H$ and $G$ then $f$ is called an isomorphism.\par

The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
of isomorphisms between $G$ and itself. 
\par

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
is called induced if $H_2$ is an induced sub-hypergraph.
We will call a labeled copy
of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
It is satisfied that the number
of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
of copies of $H$ in $G$.

The excess $ex(G)$ of an hypergraph $G$ is the number
\[
ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par

Before moving on we need to introduce some additional notation. NOTACION

Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(v,u)= \min_{\substack{H \text{ subgraph of } G\\ 
		H \text{ connected }\\
		v,u\in V(H)}} |V(H)| - 1 .\]
That is, the distance between $v$ and $u$ is the minimum size
of a connected graph $H$ containing both vertices, minus one. 
If such graph does not exist we define $d^G(u,v)=\infty$.
This definition extends naturally to subsets $X,Y\subseteq V(G)$:
\[ d^G(X,Y)=\min_{\substack{x\in X\\ y\in Y}} d^G(x,y).\]
As usual, when $X=\{x\}$ we will omit the brackets and write
$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example. When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. \par

Given set of vertices vertex, $X\subseteq V(G)$, 
we denote by $N^G(X;r)$ the $r$-neighborhood of $X$ in 
$G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
the set:
\[ Y:= \{ u \in V(G) \ | \ d(X,u)\leq r   \}. \]
In particular, when $X$ is a singleton $\{v\}$, we
will write $N^G(v;r)$ instead of $N^G(\{v\};r)$.
As before, we will usually drop the ``$G$'' from our 
notation when $G$ is understood or not relevant.

@@

Let $p_1\dots,p_t$ real numbers between zero and one,
and let $\overbar{p}=p_1,\dots,p_t$.
The random model $G^{\mathcal{C}}(n,\overbar{p})$ 
is the discrete probability space that
assigns to each hypergraph $G$ whose vertex
set $V(G)$ is $[n]$ the following probability:

\[ \mathrm{Pr}(G)=\prod_{i=1}^{t} p_i^{|E_i(G)|}
(1-p_i)^{ |E^{[n]}_{a_i,\Phi_i,P_i}|-|E_i(G)|}.	
\]
Equivalently, this is the probability space obtained by 
assigning to each edge with color $i$,  
$e\in  E^{[n]}_{a_i,\Phi_i,P_i}$ probability 
$p_i$ independently. \par

>>>>

\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\simeq_#1}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\newcommand{\ehr}{\textsc{Ehr}}
\newcommand{\PR}[1]{\mathrm{Pr}\big(#1\big)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\InR}[1]{\left\{ #1_R \right\}_{R\in \sigma}}

@@

\subsection{General notation}\label{subsect:notation}

Given a positive natural number $n$, we will write
$[n]$ to denote the set ${1,2,\dots,n}$.\par
Given a set $S$ and a natural number $k\in \N$
we will use $\binom{S}{k}$ to denote the set of 
subsets of $S$ whose size is $k$. \par
Given numbers, $n,m\in \N$ with $m\leq n$ we define
$(n)_m:=n\cdot (n-1)\cdots (n-m+1)$. Given a set
$S$ and a number $n\in \N$ with $n\leq |S|$ we define
$(S)_n$ as the subset of $S^n$ consisting of the $n$-tuples
whose coordinates are all different. 
We also define $S^*:=\bigcup_{n=0}^\infty S^n$ and
$(S)_*=\bigcup_{n\leq |S|} (S)_n$. Given a tuple 
$\overline{x}\in S^*$ and an element $x\in S$ the expression
$x\in \overline{x}$ will mean that $x$ appears as some coordinate
in $\overline{x}$. We will at times make an abuse of notation and
treat the tuple $\overline{x}$
as the set of elements $x\in \overline{x}$. \par
We will use the convention that over-lined variables
, like $\overline{x}$, denote ordered tuples of arbitrary length. 
For example, given a set $S$, if we write $\overline{x}\in S^*$
then $\overline{x}=(x_1,\dots, x_a)$ for some $a\in \N$ and 
some $x_1,\dots, x_a\in S$. Given an ordered tuple $\overline{x}$
we define the number $len(\overline{x})$ as its length. 
Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
we define $f(\overline{x})\in Y^*$ as the tuple 
$(f(x_1),\dots,f(x_a))$.
\par

Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$\overline{x}=(x_1,\dots,x_a)\in S^a$ we define 
$g\cdot(x_1,\dots,x_a)$ and $g\cdot \overline{x}$ 
as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. The notations $\overline{x}$ and
$(x_1,\dots, x_a)$ 
will be reserved 
to ordered tuples while 
$[\overline{x}]$ and
$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par
\par
Given two real functions over the natural numbers 
$f,g:\N \rightarrow \R$ we will write $f=O(g)$ to 
mean that there exists some constant $C\in \R$
such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
as usual.
If $g(n)\neq 0$ for $n$ large enough then
we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.\par

@@

A relational vocabulary $\sigma$ is a collection of
relation symbols $\{R_1,\dots, R_m,\dots\}$
where each relation symbol $R_i$ has associated a natural
number $ar(R_i)$ called its arity.
A $\sigma$-structure $\mathfrak{A}$ is composed of
a set $A$, called the universe of $\mathfrak{A}$, equipped with
relations $R_1^{\mathfrak{A}}\subseteq A^{a_1},
\dots, R_m^{\mathfrak{A}}\subseteq A^{a_m}$. When $\sigma$
is understood we may refer to $\sigma$-structures as relational
structures or simply as structures.
A structure is called finite if its universe is a finite set. \par

In the first order language $FO[\sigma]$ with signature $\sigma$ 
formulas are formed by variables $x_1,\dots,$ $x_i,\dots$,
the relation symbols in $\sigma$, the equal symbol $=$,
the usual Boolean connectives $\neg, \wedge, \vee, \dots$, 
the existential and universal quantifiers $\exists, \forall$, and
the parentheses $),($. Then formulas in $FO[\sigma]$ are defined as 
follows.
\vspace*{-0.2em}
\begin{itemize}[topsep=1pt, itemsep=1pt]
	\item The expression $R(y_1,\dots,y_a)$, where the $y_i$'s are variables and $R$
	is a relation symbol in $\sigma$ such that $ar(R)=a$,
	belongs to $FO[\sigma]$.
	\item The expression $y_1=y_2$, where $y_1, y_2$ are variables, 
	belongs to $FO[\sigma]$.
	\item Given formulas $\phi, \psi \in FO[\sigma]$, any Boolean combination of them
	$\neg(\phi), (\phi \wedge \psi), (\phi \vee \psi), \dots$ belongs to $FO[\sigma]$ as well.
	\item Given a formula $\phi \in FO[\sigma]$ and $x$ a variable that 
	does not appear bounded
	by a quantifier in $\phi$, the expressions $\forall x (\phi)$ and 
	$\exists x (\phi)$ belong both to $FO[\sigma]$. 
\end{itemize}  
We will write $\forall y_1, y_2,\dots, y_m$ or simply $\forall \overline{y}$
instead of  
$\forall y_1, \forall y_2,\dots, \forall y_m$ and likewise for
the quantifier $\exists$. Also, if $\overline{y}:=(y_1,\dots,y_a)$ is a
tuple of variables we may write simply $R(\overline{y})$ instead
of $R(y_1\dots,y_a)$.\par
For the remaining of this article we will reserve the names $x,y,z$
for the variables in our first order formulas.\par
We define the set of free variables of a formula as usual. 
Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
to denote that $\overline{y}$ is a tuple of 
(different) variables that contains all free variables in $\phi$ and
none of its bounded variables, although it may contain variables
which not appear in $\phi$. \par
Formulas with no free variables are called sentences and 
formulas with no quantifiers are called open formulas. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overline{y})$ is a
formula, $\overline{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overline{y}$ and $\overline{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overline{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overline{y}$ are interpreted as the elements in $\overline{a}$ (i.e., 
the $i$-th element of $\overline{y}$ is interpreted as the $i$-th
element of $\overline{a}$).
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

For the rest of the article consider fixed:
\begin{itemize}
	\item A relational vocabulary $\sigma$ such that all the relations $R\in\sigma$ satisfy $ar(R)\geq 2$. 
	\item 
	Groups $\overline{\Phi}=\{ \Phi_R \}_{R\in \sigma}$
	such that each $\Phi_R$ is consists of 
	permutations on $[ar(R)]$ with the usual 
	composition as its operation.	
	\item 
	Sets $\{P_R\}_{R\in \sigma}$ satisfying that for 
	all $R\in \sigma$, 
	$P_R\subseteq \binom{[ar(R)]}{2}$

@@

@@

We define the class $\mathcal{C}$ as the 
class of $\sigma$-structures that
satisfy the 
following axioms: 
\begin{itemize}
	\item \textit{Symmetry axioms}: For each $R\in \sigma$ and
	each $g\in \Phi_R$:
	\[ \forall \overline{x}:=x_1,\dots, x_{ar(R)} \big(  R(\overline{x})
	\iff R(g\cdot\overline{x}) \big)    \]
	\item \textit{Anti-reflexivity axioms}: For each 
	$R\in \sigma$ and $\{i,j\}\in P_R$
	\[ \forall x_1,\dots, x_{ar(R)} 
	\big( (x_i=x_j) \implies \neg R(x_1,\dots, x_{a_s})
	\big)\]
	\end{itemize}

We can think any structure $G$ in $\mathcal{C}$
as a "multi-hypergraph" whose vertices are the elements
of the universe of $G$. Each relation $R\in \sigma$, can be 
represented over $G$ as an "edge set" formed by tuples vertices
of size $ar(R)$ modulo the action of $\Phi_R$. Furthermore, 
repetitions of vertices in the positions given by
$P_R$ are not allowed in these tuples.\par
The following definitions make this ideas formal. They 
depend on our choices of $\sigma$, $\{\phi_R\}_{R\in \sigma}$
and $\{P_R\}_{R\in \sigma}$ but as those are fixed we can
allow ourselves to omit those dependencies for the sake of readability.

\begin{definition} 
	Let $V$ be a set, and let $R\in \sigma$.
	We define the \textbf{total edge set over $V$
	given by $R$} as
	\[ E_R[V]= (V^{ar(R)}/\Phi_R) \quad \setminus 
	\quad X, \]
	where
	\[
	X=
	\Big\{ [x_1,\dots,x_{ar(R)}]  
	\quad \Big| \quad
	x_1,\dots,x_{ar(R)}\in V, \,
	\text{ and } 
	 \, x_i=x_j \text{ for some } 
	\{i,j\}\in P_R \Big\}.
	\]
	Also, we will say that the \textbf{sort} of the elements $e\in E_R[V]$
	is $R$. 
\end{definition}

That is, $E_R[V]$ contains all the ``$ar(R)$-tuples of elements
in $V$ modulo the permutations
in $\phi_R$" 
excluding those that contain some repetition of elements in
the positions given by $P_R$.\par
The fact that the elements $e\in E_R(V)$ are of sort $R$ 
is a technical detail
introduced so that for any different relation symbols $R_1$ and
$R_2$ it holds $E_{R_1}(V)\cap E_{R_2}(V)=\emptyset$ even in the case
that $ar(R_1)=ar(R_2)$, $\Phi_{R_1}=\Phi_{R_2}$ and $P_{R_1}=P_{R_2}$.\par

In the case where $V=[n]$ we will write simply $E_R[n]$ instead
of $E_R[[n]]$.

\begin{definition} 
We call $\mathcal{C}$-\textbf{hypergraph}, or simply hypergraph, 
to a pair $G=\Big(V(G),\{E_R(G)\}_{R\in\sigma}\Big)$,
where for each $R$, $E_R(G) \subseteq E_R[V]$.
\end{definition}

Hypergraphs, as we have defined them, 
can be naturally interpreted as
structures from $\mathcal{C}$ 
in the following way: 
given $G=(V,\{E_R\}_{R\in \sigma})$,
we consider $V$ to be the universe of
 $G$, and for any $R\in \sigma$ we define
$R^G\subseteq V^{ar(R)}$ as the set of tuples
$\overline{x}\in V^{ar(R)}$ such that
$[\overline{x}]\in E_R$. Under 
this interpretation hypergraphs
satisfy by definition the 
symmetry and anti-reflexivity
axioms given at the beginning of this section. It is also easy to
see that this interpretation induces
a one-to-one identification between 
structures in $\mathcal{C}$ and hypergraphs. \par

\subsection{Hypergraph notation and nomenclature}

We will use standard nomenclature and notation
from graph theory with some additions. Given an 
hypergraph $G$ we will call its \textbf{vertex set} to $V(G)$ 
and \textbf{vertices} 
to the elements $v\in V(G)$. Likewise, each of 
the $E_R(G)$'s will be called an \textbf{edge set} and its elements, 
\textbf{edges}. Given an edge set $E_R(G)$, 
the index $R$ will be called its \textbf{relation}.

\par
Given an hypergraph $G$ we define the set $E(G)$ as the
union $\cup_{R\in \sigma}E_R(G)$. Notice that this union 
is disjoint because elements from different $E_R(G)$'s 
are of different sorts. Thus, $|E(G)|=\sum_{R\in \sigma} 
|E_R(G)|$. Analogously, given a set $V$, we define
$E[V]:=\cup_{R\in \sigma} E_R[V]$.
Given an edge $e\in E[V]$ we define $R(e)$
as the sort of $e$, i.e.,
the unique relation symbol $R(e)\in \sigma$
such that $e\in E_{R(e)}[V]$.

Given two hypergraphs $H$ and $G$ we say that $H$
is a \textbf{sub-hypergraph} of $G$, which we write as $H\subset G$,
if $V(H)\subset V(G)$ and $E(H)\subset E(G)$ (notice 
that this is equivalent to $E_R(H)\subset E_R(G)$ for all
$R\in \sigma$, since the edges are sorted).\par

Given a set of vertices $U\subseteq V(G)$, 
we will denote by $G[U]$ the \textbf{hypergraph induced
by $G$ on $U$}. That is, $G[U]$ is an hypergraph
$H=(V(H),\{E(H)_R\}_{R\in \sigma})$ such that 
$V(H)=U$ and for any $R\in \sigma$ 
each edge $e\in E_R(G)$ belongs 
to $E_R(H)$ as well if and only if the vertices
involved in $e$ are in $U$ (i.e. $e\in E_R[U]$).
\par
%
%An homomorphism between two hypergraphs $G$ and $H$ 
%a map $f:V(G)\rightarrow V(H)$ that sends edges 
%from $G$ to edges in $H$ of the same color. That is,
%if vertices $v_1,\dots, v_{a_i}$ form an edge 
%$[v_1,\dots,v_{a_i}]\in E_i(G)$, then
%$[f(v_1),\dots,f(v_{a_i})]\in E_i(H)$.
%If $f$ is injective then it is called a monomorphism. 
%If $f$ is bijective and its inverse is also an homomorphism 
%between $H$ and $G$ then $f$ is called an isomorphism.\par
%
%The group of automorphisms $Aut(G)$ of an hypergraph $G$ is the group
%of isomorphisms between $G$ and itself.

%
%Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
%a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
%is called induced if $H_2$ is an induced sub-hypergraph.
%We will call a labeled copy
%of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
%It is satisfied that the number
%of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
%of copies of $H$ in $G$.

We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
\[
ex(G):= \big(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par

Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
		H \text{ connected }\\
		u,v\in V(H)}} |E(H)| .\]
That is, the distance between $v$ and $u$ is the minimum number of
edges necessary to connect $v$ and $u$. 
If such number does not exist we define $d^G(u,v)=\infty$. \par
As usual, define $d^{G}(X,Y)$ for sets $X,Y\subset V(G)$ as the minimum
distance $d(u,v)$ where $u\in X$ and $v\in Y$. 
When $X=\{x\}$ we will omit the brackets and write
$d^G(x,Y)$ instead of $d^G(\{x\},Y)$, for example.
When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. \par

Given set of vertices vertex, $X\subseteq V(G)$, 
we denote by $N^G(X;r)$ the $r$-\textbf{neighborhood} of $X$ in 
$G$. That is,  $N^G(X;r)= G[Y]$, where $Y\subseteq V(G)$ is 
the set:
\[ Y:= \{ u \in V(G) \ | \ d(X,u)\leq r   \}. \]
In particular, when $X$ is a singleton $\{v\}$, we
will write $N^G(v;r)$ instead of $N^G(\{v\};r)$.
As before, we will usually drop the ``$G$'' from our 
notation when $G$ is understood or not relevant.  \par

We will often write tuples of vertices instead of sets
inside of $d(\cdot\, , \cdot)$ and $N(\cdot\, ;r)$. In those cases
we are treating those tuples as sets as specified in
\cref{subsect:notation}.

@@

For each $R\in \sigma$ let
$p_R$ be a real number between zero and one.
Let $\overline{p}:=\InR{p}$.
The random model $G^{\mathcal{C}}(n,\overline{p})$ 
is the discrete probability space that
assigns to each hypergraph $G$ whose vertex
set $V(G)$ is $[n]$ the following probability:

\[ \mathrm{Pr}(G)=\prod_{R\in \sigma} p_R^{|E_R(G)|}
(1-p_R)^{ \big|E_R[n]\big|-\big|E_R(G)\big|}.	
\]
Equivalently, this is the probability space obtained by 
assigning to each edge $e\in E_R[n]$ probability 
$p_R$ independently. \par

%Let $G_n$ denote a random hypergraph in 
%$G^\mathcal{C}(n,\overline{p})$, where 
%$\bar{p}:=p_1,\dots,p_t$, and 
%we allow each $p_i$ to depend on $n$. 
As in the case of Lynch's theorem, we are interested in the
"sparse regime" of $G^\mathcal{C}(n,\overline{p})$, were the 
expected number of edges each color is linear. 
%In other words, we want that
%$\mathrm{E}[m_i(G_n)]=\Theta(n)$ for all $i$'s.
This is achieved when each of the $p_R$'s are 
of the form $\beta_R/n^{ar(R)-1}$ for some 
non-negative real numbers $\InR{\beta}$.
From now on we will write $G_n\left(\InR{\beta}\right)$
to denote a random sample of 
$G^\mathcal{C}\left(n,\left\{ \frac{
\beta_R}{n^{ar(R)-1}}\right\}_{R\in\sigma}\right)$.
When the choice of $\InR{\beta}$ is not relevant
we will write $G_n$ instead of 
$G_n\left(\InR{\beta}\right)$.\par
